---
title: "Data Process"
author: "Thicc Data Team"
date: "March 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(rlang)
```

```{r}
raw <- readr::read_csv("dataFestReleaseFinal_3_23.csv")
```

### Question: Supply and Demand in Different Employer Industries
```{r data_industry, warning = FALSE}
# group_by jobHash
raw_unique1 <- raw %>%
  select(applies, clicks, employerIndustry, jobHash) %>%
  group_by(jobHash) %>%
  summarize(total_applies = sum(applies),
            total_clicks = sum(clicks),
            industry = first(employerIndustry)) %>%
  group_by(industry) %>%
  summarize(num_jobs = n(),
            num_applies = sum(total_applies),
            num_clicks = sum(total_clicks)) %>%
  mutate(ratio_apply = num_applies/num_jobs,
         ratio_click = num_clicks/num_jobs) 
```

### Draw data graphic to show the ratio of applies and clicks over job postings across all industries: Which industry is the most competitive?
```{r ratio_graph, warning = FALSE}
raw_unique1 %>% ggplot(aes(x = reorder(industry, -ratio_apply))) +
  geom_bar(aes(y = ratio_apply), stat = "identity", fill = rgb(224/255, 132/255, 13/255)) +
  labs(title = "Average number of applies and clicks per job across industries") +
  theme(axis.text.x = element_text(face = "bold", size = 10, angle = 45), 
        axis.text.y = element_text(face = "bold", size = 10), 
        axis.title.x = element_text(face = "bold", size = 10), 
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(face = "bold", size = 10)) + 
  scale_x_discrete(name = "Industry") +
  scale_y_continuous(name = "Counts", labels = scales::comma)  
```

### Draw data graphic to show the total number of job postings across all industries: which industry hires the most?
```{r postings_graph}
raw_unique1 %>% ggplot(aes(x = reorder(industry, -num_jobs))) +
  geom_bar(aes(y = num_jobs), stat = "identity", fill = rgb(22/255, 199/255, 102/255)) +
  labs(title = "Number of job postings across industries") +
  theme(axis.text.x = element_text(face = "bold", size = 10, angle = 45), 
        axis.text.y = element_text(face = "bold", size = 10), 
        axis.title.x = element_text(face = "bold", size = 10), 
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(face = "bold", size = 10)) + 
  scale_x_discrete(name = "Industry") +
  scale_y_continuous(name = "Counts", labels = scales::comma)  
```

### Question: (1) Across different industries, which methods of advertising is more popular (Direct Employer or Third Party (Staffing Agencies or Job Boards))







```{r edu}
# Investigating the association between education requirements and application numbers

# Cleaning up the data
edu <- raw %>% 
  select(jobHash, licenseRequiredJob, 
         noEducationRequirementsJob, 
         highSchoolEducationRequirementsJob, 
         higherEducationRequirementsJob, applies) %>% 
  group_by(jobHash) %>% 
  mutate(ttl_app = sum(applies), 
         license = max(licenseRequiredJob), 
         none = max(noEducationRequirementsJob), 
         highschool = max(highSchoolEducationRequirementsJob), 
         higher = max(highSchoolEducationRequirementsJob)) %>% 
  filter(row_number()==1)

edu <- edu %>% 
  select(jobHash, ttl_app, none, license, highschool, higher)


# Exploratory analysis
## how many jobs
edu_req <- edu %>% 
  ungroup() %>% 
  summarize(none = sum(none), license = sum(license), 
            highschool = sum(highschool), higher = sum(higher, na.rm = TRUE)) %>% 
  gather(key = reqtype, value = n)
plot_req_n <- ggplot(edu_req, aes(x = reqtype, y = n)) + geom_bar(stat = "identity")

## reqs versus apps
edu_none <- edu %>% 
  filter(none == 1) %>% 
  ungroup() %>% 
  summarise(app_none = sum(ttl_app))
edu_license <- edu %>% 
  filter(license == 1) %>% 
  ungroup() %>% 
  summarise(app_license = sum(ttl_app))
edu_highsch <- edu %>% 
  filter(highschool == 1) %>% 
  ungroup() %>% 
  summarise(app_highsch = sum(ttl_app))
edu_higher <- edu %>% 
  filter(higher == 1) %>% 
  ungroup() %>% 
  summarise(app_higher = sum(ttl_app))
### plot it
edu_req_app <- edu_req %>% 
  mutate(app = c(edu_none$app_none, edu_license$app_license, 
                 edu_highsch$app_highsch, edu_higher$app_higher), 
         mean_app = app/n)
plot_req_app <- ggplot(edu_req_app, aes(x = reqtype, y = app)) + geom_bar(stat = "identity")
plot_req_app_mean <- ggplot(edu_req_app, aes(x = reqtype, y = mean_app)) + 
  geom_bar(stat = "identity")

## predict number of applications with jobreqs
m_edu_app_req <- lm(ttl_app~none+license+highschool, data = edu)
summary(m_edu_app_req)
```
