---
title: "Data Process"
author: "Thicc Data Team"
date: "March 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(rlang)
library(RColorBrewer)
```

```{r}
raw <- readr::read_csv("dataFestReleaseFinal_3_23.csv")
```

## Question: Supply and Demand in Different Employer Industries
```{r data_industry, warning = FALSE}
# group_by jobHash
industry_table <- raw %>%
  select(applies, employerIndustry, jobHash, supervisingJob) %>%
  group_by(jobHash) %>%
  summarize(total_applies = sum(applies),
            industry = first(employerIndustry),
            supervisingJob = first(supervisingJob)) %>%
  group_by(industry) %>%
  summarize(num_jobs = n(),
            num_applies = sum(total_applies), 
            num_supervising_jobs = sum(supervisingJob)) %>%
  mutate(ratio_apply = num_applies/num_jobs) 
```

### Draw data graphic to show the total number of job postings across all industries: which industry hires the most?
```{r postings_graph}
industry_table %>% ggplot(aes(x = reorder(industry, -num_jobs))) +
  geom_bar(aes(y = num_jobs), stat = "identity", fill = rgb(22/255, 199/255, 102/255)) +
  geom_bar(aes(y = num_supervising_jobs), stat = "identity", fill = "red") +
  labs(title = "Number of job postings across industries") +
  theme(axis.text.x = element_text(face = "bold", size = 10, angle = 45), 
        axis.text.y = element_text(face = "bold", size = 10), 
        axis.title.x = element_text(face = "bold", size = 10), 
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(face = "bold", size = 10)) + 
  scale_x_discrete(name = "Industry") +
  scale_y_continuous(name = "Counts", labels = scales::comma)  
```

### Draw data graphic to show the ratio of applies over job postings across all industries: Which industry is the most competitive?
```{r ratio_graph, warning = FALSE}
industry_table %>% ggplot(aes(x = reorder(industry, -ratio_apply))) +
  geom_bar(aes(y = ratio_apply), stat = "identity", fill = rgb(224/255, 132/255, 13/255)) +
  labs(title = "Average number of applies per job across industries") +
  theme(axis.text.x = element_text(face = "bold", size = 10, angle = 45), 
        axis.text.y = element_text(face = "bold", size = 10), 
        axis.title.x = element_text(face = "bold", size = 10), 
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(face = "bold", size = 10)) + 
  scale_x_discrete(name = "Industry") +
  scale_y_continuous(name = "Counts", labels = scales::comma)  
```

## Question: Across different industries, which methods of advertising is more popular (Direct Employer or Third Party (Staffing Agencies or Job Boards))
```{r}
# filter out companies that we don't know what type of advertising they used
ad_table <-  raw %>% 
  select(applies, employerIndustry, jobHash, advtype, employeecount) %>%
  filter(advtype == "Direct Employer" | advtype == "Staffing Agency" | advtype == "Job Boards") %>% 
  mutate(ad = ifelse(advtype == "Direct Employer", "Direct Employer", "Third Party")) %>%
  select(-advtype)

ad_table_a <- ad_table %>%
  group_by(employerIndustry, ad) %>%
  summarize(num_jobs_per_method = n(),
            num_applies_per_method = sum(applies))

ad_table_b <- ad_table %>%
  group_by(employerIndustry) %>%
  summarize(total_jobs = n(), 
            total_applies = sum(applies))

ad_table <- ad_table_a %>%
  inner_join(ad_table_b, by = "employerIndustry") %>%
  mutate(p_jobs = num_jobs_per_method/total_jobs,
         p_applies = num_applies_per_method/total_applies) %>%
  group_by(employerIndustry) %>%
  mutate(p_jobs_third_party = last(p_jobs))
```

```{r}
# plot for jobs
ad_table %>% ggplot(aes(x = reorder(employerIndustry, -p_jobs_third_party))) +
  geom_bar(aes(y = p_jobs, fill = factor(ad)), stat = "identity") +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(face = "bold", size = 10, angle = 45), 
        axis.text.y = element_text(face = "bold", size = 10), 
        axis.title.x = element_text(face = "bold", size = 10), 
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(face = "bold", size = 10)) + 
  scale_x_discrete(name = "Industry") +
  scale_y_continuous(name = "Percentage", labels = scales::percent)  
  
```

## Question 3: Distribution of jobs among different sizes of companies
```{r}
size_table <- raw %>%
  select(applies, employeecount, jobHash) %>%
  group_by(jobHash) %>%
  summarize(num_applies = sum(applies),
            size = first(employeecount)) %>%
  group_by(size) %>%
  summarize(num_jobs = n(),
            total_applies = sum(num_applies))
  
```


```{r}
size_table %>% ggplot(aes(x = size)) +
  geom_bar(aes(y = total_applies),stat = "identity") +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(face = "bold", size = 10, angle = 45), 
        axis.text.y = element_text(face = "bold", size = 10), 
        axis.title.x = element_text(face = "bold", size = 10), 
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(face = "bold", size = 10)) + 
  scale_x_discrete(name = "Size") +
  scale_y_continuous(name = "Percentage", labels = scales::percent) 
```

